Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-08-02 TitlePage.tex
Add dedication page
Add page number to dedication page
TitlePage: Dissertationsentwürf -> Dissertation
Remove wrong sentence spaces in titlepage

\begin{titlepage}
% Declarations, in scope until \end{titlepage}.
\makeatletter % for \@title and \@author
\setlength{\parskip}{0pt}
\centering
\large
%
% https://tex.stackexchange.com/a/241121/1340
\linespread{1.5}\selectfont
\sffamily
% Slanted because no real \itshape available for this font
% (https://tex.stackexchange.com/a/68932/1340).
\slshape
% Huge titles are broken by cm-super. Using lmodern locally fixes it.
\fontfamily{lmss}
\selectfont

@@

{Dissertations\/\bfseries\upshape entwurf}\\
der Mathematisch- und Naturwissenschaftlichen Fakult\"at\\
der Eberhard Karls Universit\"at T\"ubingen\\
zur Erlangung des Grades eines\\
Doktors der Naturwissenschaften\\
(Dr. rer. nat.)

@@

\vfill
\end{titlepage}
% TODO: insert here page 2 with the needed thesis boilerplate.
%\clearpage

>>>>

\begin{titlepage}
% Declarations, in scope until \end{titlepage}.
\makeatletter % for \@title and \@author
\setlength{\parskip}{0pt}
\centering
\large
%
% https://tex.stackexchange.com/a/241121/1340
\linespread{1.5}
\sffamily
% Slanted because no real \itshape available for this font
% (https://tex.stackexchange.com/a/68932/1340).
\slshape
% Huge titles are broken by cm-super. Using lmodern locally fixes it.
\fontfamily{lmss}
\selectfont

@@

{\bfseries Dissertation}\\
der Mathematisch- und Naturwissenschaftlichen Fakult\"at\\
der Eberhard Karls Universit\"at T\"ubingen\\
zur Erlangung des Grades eines\\
Doktors der Naturwissenschaften\\
(Dr.\ rer.\ nat.)

@@

\vfill
\end{titlepage}
\clearpage
% TODO: insert here page 2 with the needed thesis boilerplate.
\cleardoublepage
{%
\begin{flushright}
  \null\vspace{\stretch{1}}
  To the memory of my mother Rosalia\\
  ~\\
  Alla memoria di mia madre Rosalia

  \vspace{\stretch{3}}
  \null
\end{flushright}}
